Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-27 autovi_paper.qmd
update implementation details

The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system. This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding XXX I think the technical term is overloading? XXX. While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package. XXX Not sure if this last sentence is necessary XXX

>>>>

The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system. This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding.

### 2024-11-27 autovi_paper.tex
update implementation details

The \texttt{autovi} package is built on the \texttt{bandicoot}
object-oriented programming (OOP) system \citep{bandicoot}, marking a
departure from R's traditional S3 generic system. This OOP architecture
enhances flexibility and modularity, allowing users to redefine key
functions through method overriding XXX I think the technical term is
overloading? XXX. While similar functionality could be achieved using
R's S3 system with generic functions, the OOP framework offers a more
structured and extensible foundation for the package. XXX Not sure if
this last sentence is necessary XXX

>>>>

The \texttt{autovi} package is built on the \texttt{bandicoot}
object-oriented programming (OOP) system \citep{bandicoot}, marking a
departure from R's traditional S3 generic system. This OOP architecture
enhances flexibility and modularity, allowing users to redefine key
functions through method overriding.
